Income and Food Price Transmission\footnote{Revised version of MS 2015310 ``Income and Price Transmission''. Submitted to \emph{Agricultural Economics} for 2. round review. I thank two anonymous reviewers for their valuable comments.}

### 2016-03-02 figures.Rnw
Revised figures script. Used for 2. round rev. version of paper

dat = read.csv("dist_trade.csv", sep = ";")
dat$gamma = (dat$vop_covx+dat$vop_covm)/dat$vop_covt*100
ggplot(dat, aes(log(gdppcp00), gamma)) + 
  geom_point() + 
  geom_smooth() +
  theme_bw() +
  xlab("Log of GDP") +
  ylab(expression(paste("Estimated ", gamma))) +
  theme(panel.grid.major = element_line(colour = "grey"))
@

@@

p2 = ggplot(aes(x=foodinfl78, y=foodinfl1011), data = infl) + 
  geom_point(shape=1) +
  geom_smooth(method=loess) +
  theme_bw() +
  ylab("FPI inflation 2010-11") + 
  xlab("FPI inflation 2007-08") +
  geom_text(aes(label=ifelse(foodinfl78>40,as.character(iso3c),'')),hjust=1.2,just=-1.2, 
            size=3) +
  geom_text(aes(label=ifelse(foodinfl1011>20,as.character(iso3c),'')),hjust=1.2,just=-1.2,
            size=3)

p3 = ggplot(aes(x=cpiinfl78, y=cpiinfl1011), data = infl) +
  geom_point(shape=1) +
  geom_smooth(method=loess) +
  theme_bw() +
  ylab("CPI inflation 2010-11") + 
  xlab("CPI inflation 2007-08") +
  geom_text(aes(label=ifelse(cpiinfl78>30,as.character(iso3c),'')),hjust=1.2,just=-1.2, 
            size=3) +
  geom_text(aes(label=ifelse(cpiinfl1011>15,as.character(iso3c),'')),hjust=1.2,just=-1.2,
            size=3)

p4 = ggplot(aes(x=rfpigr78, y=rfpigr1011), data = infl) + 
  geom_point(shape=1) +
  geom_smooth(method=loess) +
  theme_bw() +
  ylab("Real FPI growth 2010-11") + 
  xlab("Real FPI Growth 2007-08") +
  geom_text(aes(label=ifelse(rfpigr78>12,as.character(iso3c),'')),hjust=1.2,just=-1.2, 
            size=3) +
  geom_text(aes(label=ifelse(rfpigr1011>10,as.character(iso3c),'')),hjust=1.2,just=-1.2,
            size=3)

>>>>

## Import data into R.
str = "C:/Users/nqw235/Google Drev/Research/pov_price_transmission/"
temp = paste(str, "dist_trade.csv", sep = "")

dat = read.csv(temp, sep = ";")
dat$gamma = (dat$vop_covx+dat$vop_covm)/dat$vop_covt*100
ggplot(dat, aes(log(gdppcp00), gamma)) + 
  geom_point() + 
  geom_smooth() +
  theme_bw() +
  xlab("Log of GDP") +
  ylab(expression(paste("Estimated ", gamma))) +
  theme(panel.grid.major = element_line(colour = "grey"))
@

@@

p2 = ggplot(aes(x=foodinfl78, y=foodinfl1011), data = infl) + 
  geom_point(shape=1) +
  geom_smooth(method=loess) +
  theme_bw() +
  ylab("FPI inflation 2010-11") + 
  xlab("FPI inflation 2007-08") +
  geom_text(aes(label=ifelse(foodinfl78>40,as.character(iso3c),'')),hjust=1.2,vjust=-1.2, 
            size=3) +
  geom_text(aes(label=ifelse(foodinfl1011>20,as.character(iso3c),'')),hjust=1.2,vjust=-1.2,
            size=3)

p3 = ggplot(aes(x=cpiinfl78, y=cpiinfl1011), data = infl) +
  geom_point(shape=1) +
  geom_smooth(method=loess) +
  theme_bw() +
  ylab("CPI inflation 2010-11") + 
  xlab("CPI inflation 2007-08") +
  geom_text(aes(label=ifelse(cpiinfl78>30,as.character(iso3c),'')),hjust=1.2,vjust=-1.2, 
            size=3) +
  geom_text(aes(label=ifelse(cpiinfl1011>15,as.character(iso3c),'')),hjust=1.2,vjust=-1.2,
            size=3)

p4 = ggplot(aes(x=rfpigr78, y=rfpigr1011), data = infl) + 
  geom_point(shape=1) +
  geom_smooth(method=loess) +
  theme_bw() +
  ylab("Real FPI growth 2010-11") + 
  xlab("Real FPI Growth 2007-08") +
  geom_text(aes(label=ifelse(rfpigr78>12,as.character(iso3c),'')),hjust=1.2,vjust=-1.2, 
            size=3) +
  geom_text(aes(label=ifelse(rfpigr1011>10,as.character(iso3c),'')),hjust=1.2,vjust=-1.2,
            size=3)
